Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-08-30 Paperfolder/MDPI_submission/Revision01/Response/Response to the reviewers/Response to the reviewers.Rmd

[Response:] Thanks for the pertinent comment. Although we conducted the presenty analyses in men and women separately from the beginning based our previous finding from the same cohort as well as on a prior finding from the Singapre Chinese Health Study, the rationale might not have have been clear. We have revised the manuscript (Methods) incorporating the point. Nevertheless, a test of interaction for milk intake by sex indicated significant interaction (using traditional likelihood ratio test comparing Cox proportional hazard models with and without the interaction terms between sex and milk intake frequencies, P < 0.0001, not shown in the main test). Stratified analyses by sex also suggested the directions of AFs and HRs differ in a few frequency categories (Table 2 and 3, results in the "total stroke" parts).

We have also added possible explanations for the sex-interaction in the Discussion.

- *#4: The aim states to “provide a more straightforward answer to the primary research question” – compared to what? And how is this more straightforward answer achieved. This is not clear, neither in the aim nor in the discussion (lines166-167). Please revise.*

[Response:] Thanks for the useful suggestion. We meant that the Bayesian approach would provide more straightforward answer compared to traditional statistical approach. We have added clearer descriptions about these research questions and interpretations in Introduction and Discussion.

@@

- *Please describe the context of milk intake in Japan. Is milk consumed as a beverage with food, added to coffee or other consumption patterns? Are other milk products than fresh non-fermented milk consumed and could be included in the “milk” exposure?*

[Response:] We appreciate the reviewer's great points. During the baseline years of the JACC study (between 1988 and 1990), most "milk and dairy product" consumption (92.1%) was in the form of whole milk. We have added the context of milk intake in Japan for participants who were invited into the JACC study. For detailed description about more current situation, as we cited in the Introduction (Reference #4, as cited below), the per capta consumption is still much lower than that in the western population:

Saito, A.; Okada, E.; Tarui, I.; Matsumoto, M.; Takimoto, H. The Association between Milk and Dairy Products Consumption and Nutrient Intake Adequacy among Japanese Adults: Analysis of the 2016 National Health and Nutrition Survey. Nutrients 2019, 11, 2361.

@@

- *Please specify age at baseline in abstract and methods.*

[Response:] Age range are now added in the abstract and methods accordingly.

- *Outcome ascertainment: Information on cause of death was from death certificates. Is there a possibility of individual linkage of the FFQ responses to a cause of death registry or were each of the participants’ death certificates reviewed? How many died from other causes, how many moved from the study area (and were thus lost to follow-up) and how many were censored at the end of follow-up (alive). Has stroke mortality changed during follow-up? Is there a difference in time trends of stroke subtype mortality? In how many cases was stroke subtype not recorded? The authors should also discuss potential reasons for differences in the results for stroke subtypes.*

[Response:] We are grateful to the reviewer's suggestion. We have added these detailed information at the beginning of the Results section. In the study area, investigators conducted systematic review of death certificates till the end of 2009. Date and cause of death were confirmed with the permission of the Director-General of the Prime Minister's Office. Number of deaths from causes other than stroke were 18868 (10731 men and 8137 women); 5493 (2022 men and 3471 women) dropped out from the follow-up (5.8%); 67349 (25281 men and 42068 women) were censored at the end of follow-up (71.4%). Among the 2675 stroke mortality confirmed in the JACC study, 766 were unfortunately not recorded with subtypes. The median (IQR) of follow-up years for cerebral infarction mortality were 11.2 (7.1, 15.3) and 11.8 (7.9, 16.4) in men and women; the median (IQR) of follow-up years for hemorrhagic stroke mortality were 9.9 (5.4, 12.3) and 10.9 (5.9, 15.1) in men and women. Potential reasons for differences in the results for stroke subtypes are described in discussion.

@@

- *I agree with the authors that presenting the results in the FFQ categories is a good option, rather than to calculate the amount of consumption. However, I wonder if there is some indication from the validation study as to how much is on average consumed in the higher categories of intake?*

[Response:] Thanks for the suggestion. The validation study of the FFQ used in the JACC study found that the median intake for a milk consumer was about 146 grams per day. This has been added in the first paragraph of "2.2 Exposure and the outcome of interest" section.

@@

- *Why did you adjust for sleep duration, is that a factor that influences both milk intake and stroke mortality risk?*

[Response:] Thanks for pointing this out. A previous report from the JACC Study (cited as below) showed that healthy lifestyle behaviors are closely related with each other and (including milk intake daily and proper sleep duration) were associated with CVD mortality. Therefore, we also included sleep duration as one of the potential confounders.

### 2020-08-30 Paperfolder/Paperfolder.Rmd
updated revision submitted

  The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population. We used data from the Japan Collaborative Cohort (JACC) Study (total number of participants = 110585, age range: 40-79) to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline. These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process. 100000 posterior samples were generated separately through four independent chains after model convergency was confirmed. Posterior probabilites that daily milk consumers had lower hazard or delayed mortality from strokes compared to non-consumers was 99.0% and 78.0% for men and women, respectively. Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC study has provided strong evidence that daily milk intake among Japanese men was associated with delayed and lower hazard of mortality from stroke especially cerebral infarction.

@@

Eastern Asian populations were reported to have higher burden from both mortality and morbidity from stroke than populations in European or American regions [@Kim2014]. Dairy foods, especially milk has been suggested to related with decreased stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in Western countries [@Saito2019]. Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], it would be of interest to provide information on the association within a context that most individuals have much lower range of milk intake compared to most of the previous studies. Whether people with such a low level intake of milk can still benefit against stroke would require elucidation.

Moreover, a more intuitive or straightforward interpretation would be available if we were able to show the probabilities and the certainty that the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke. This would require transformation of the research question into "Do individuals with milk intake habit have lower hazard of dying from a stroke event?" Another way of asking the same research question would be "Can a event of dying from stroke be postponed by having a milk intake habit?" The later question is indeed directly comparing the length of times before events or the speed from the same departure point (entry of the study) to a fatal stroke event. Accelerated failure time models (AFT) under Bayesian framework are convenient tools that would help avoid worrying about the assumptions of repeatability of a large scale prospective study, and can calculate the exact proportion of posterior estimates (hazard ratios, HR) that is lower than 1. AFT model is helpful in estimating acceleration factors (AF) which can be interpreted as the velocity for developing an event of interest. This velocity parameter shows how faster/slower individuals in one exposure group might have an event compared to others in different exposure groups [@Wei1992;@ibrahim2014b].

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was sponsored by the Ministry of Education, Sports, Science, and Technology of Japan. Sampling methods and details about the JACC study have been described extensively in the literature [@Ohno2001; @Tamakoshi2005; @Tamakoshi2013]. Participants of the JACC study completed self-administered questionnaires about their lifestyles, food intake (food frequency questionnaire, FFQ), and medical histories of cardiovascular disease or cancer. In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) who aged between 40-79 at the baseline year were successfully retained for the current analysis. We further excluded samples if they meet one of the following criteria: 1) with any disease history of stroke, cancer, myocardial infarction, ischemic heart disease, or other types heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the question regarding their milk consumption in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally, 94385 (39386 men and 54999 women) are left in the database. The study design and informed consent procedure were approved by the Ethics Review Committee of Hokkaido University School of Medicine.

@@

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models. Velocities that milk consumers dying from stroke is slower by a crude acceleration factor (AF) between 0.79 (SD = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers. Chances that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month

@@

\noindent was higher than 86.5% in men and greater than 94.6% in women. However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers. Specifically, the mean (SD; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (SD = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (SD = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (SD = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (SD = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.

>>>>

  The aim was to further examine the relationship between milk intake and stroke mortality among the Japanese population. We used data from the Japan Collaborative Cohort (JACC) Study (total number of participants = 110585, age range: 40-79) to estimate the posterior acceleration factors (AF) as well as the hazard ratios (HR) comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline. These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process. 100000 posterior samples were generated separately through four independent chains after model convergency was confirmed. Posterior probabilites that daily milk consumers had lower hazard or delayed mortality from strokes compared to non-consumers was 99.0% and 78.0% for men and women, respectively. Accordingly, the estimated posterior means of AF and HR for daily milk consumers were 0.88 (95% Credible Interval, CrI: 0.81, 0.96) and 0.80 (95% CrI: 0.69, 0.93) for men and 0.97 (95% CrI: 0.88, 1.10) and 0.95 (95% CrI: 0.80, 1.17) for women. In conclusion, data from the JACC study provided strong evidence that daily milk intake among Japanese men was associated with delayed and lower hazard of mortality from stroke especially cerebral infarction.

@@

Eastern Asian populations were reported to have higher burden from both mortality and morbidity from stroke than populations in European or American regions [@Kim2014]. Dairy foods, especially milk has been suggested to relate with decreased stroke risk by nearly 7% for each 200 g increment of daily consumption [@DeGoede2016]. Although 2 daily servings of milk or dairy products is recommended in Japan [@Yoshiike2007], the actual per capita intake ($\approx$ 63 g/day) of these food groups is much lower and less frequent than that in Western countries [@Saito2019]. Given that previous reports have also indicated no significant [@Iso1999;@sauvaget2003intake;@Elwood2004] or even positive associations [@Larsson2009], it would be of interest to provide information on the association within a context that most individuals have much lower range of milk intake compared to most of the previous studies. Whether people with such a low level intake of milk can still benefit against stroke would require elucidation.

Moreover, a more intuitive or straightforward interpretation would be available if we were able to show the probabilities and the certainty that the existing data can provide evidence about whether drinking milk can delay or lower the hazard of dying from stroke. This would require transformation of the research question into "Do individuals with milk intake habit have lower hazard of dying from a stroke event?" Another way of asking the same research question would be "Can a event of dying from stroke be postponed by having a milk intake habit?" The later question is directly comparing the length of times before events or the speed from the same departure point (entry of the study) to a fatal stroke event. Accelerated failure time models (AFT) under Bayesian framework are convenient tools that would help avoid worrying about the assumptions of repeatability of a large scale prospective study, and can calculate the exact proportion of posterior estimates (hazard ratios, HR) that is lower than 1. AFT model is helpful in estimating acceleration factors (AF) which can be interpreted as the velocity for developing an event of interest. This velocity parameter shows how faster/slower individuals in one exposure group might have an event compared to others in different exposure groups [@Wei1992;@ibrahim2014b].

@@

We used data from the Japan Collaborative Cohort (JACC) study, which was sponsored by the Ministry of Education, Sports, Science, and Technology of Japan. Sampling methods and details about the JACC study have been described extensively in the literature [@Ohno2001; @Tamakoshi2005; @Tamakoshi2013]. Participants of the JACC study completed self-administered questionnaires about their lifestyles, food intake (food frequency questionnaire, FFQ), and medical histories of cardiovascular disease or cancer. In the final follow-up of the JACC study, data from a total of 110585 individuals (46395 men and 64190 women) who aged between 40-79 at the baseline were successfully retained for the current analysis. We further excluded samples if they meet one of the following criteria: 1) with any disease history of stroke, cancer, myocardial infarction, ischemic heart disease, or other types heart disease (n = 6655, 2931 men and 3724 women); 2) did not answer the question regarding their milk consumption in the baseline FFQ survey (n = 9545, 3593 men and 5952 women). Finally, 94385 (39386 men and 54999 women) are left in the database. The study design and informed consent procedure were approved by the Ethics Review Committee of Hokkaido University School of Medicine.

@@

Detailed results from the Bayesian survival models (crude, age-adjusted and multivariable-adjusted) according to the frequency of milk intake separated by sex are listed in \textbf{Table \ref{tab:tab2}} (men) and \textbf{Table \ref{tab:tab3}} (women). Compared to those who never had milk, both men and women had slower speed and lower hazard of dying from total stroke in crude models. Velocities that milk consumers dying from stroke was slowed down by a crude acceleration factor (AF) between 0.79 (SD = 0.05; 95% CrI: 0.74, 0.90) and 0.93 (SD = 0.04; 95% CrI: 0.85, 1.02) compared with non-consumers. Chan-

@@

\noindent  ces that the posterior crude HRs were estimated to be lower than 1 for those who had at least 1-2 times/month was higher than 86.5% in men and greater than 94.6% in women. However, lower hazard and delayed time-to-event was observed to remain after age or multivariable adjustment only among daily male milk consumers. Specifically, the mean (SD; 95% CrI) of posterior multivariable-adjusted AF and HR for daily male consumers of milk were 0.88 (SD = 0.05; 95% CrI: 0.81, 0.96) and 0.80 (SD = 0.07; 95% CrI: 0.69, 0.93) with a probability of 99.0% to be smaller than the null value (=1). Daily female milk consumers had posterior AFs and HRs that were distributed with means of 0.97 (SD = 0.09; 95% CrI: 0.88, 1.10) and 0.95 (SD = 0.12; 95% CrI: 0.80, 1.17) which had about 78.0% of chance that their HRs could be smaller than 1.
